---
title: "Measles dictionary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Measles dictionary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```

# Variables in the dictionary

The Measles dictionary contains definitions for `r nrow(epidict::msf_dict("Measles"))` variables:

```{r measles, results="asis"}
library(epidict)
measles <- msf_dict("Measles")
names_desc <- measles[c("data_element_formname", "data_element_shortname", "data_element_description", "data_element_valuetype")]
DT::datatable(names_desc)
```

# Option codes

The dictionaries are exported using option codes that can be translated to
human-readable format. This table shows how they are translated.

```{r measles_values, results = "asis"}
meas <- tidyr::unnest(measles, cols = options)[c("data_element_shortname", "data_element_valuetype", "option_code", "option_name", "option_order_in_set")]
DT::datatable(meas)
```

# Exploring the data set

You can explore the original data set with `browseURL(system.file("extdata", "MSF-outbreak-dict.xlsx", package = "epidict"))`, but treat it as read-only.

