The goal of {epidict} is to provide standardized data dictionaries for the MSF 
R4EPIs project. Learn more about R4EPIs at <https://r4epis.netlify.com>

## Installation

You can install {epidict} from CRAN:

``` r
install.packages("epidict")
```

<details>
<!--
NOTE: everything inside the details tag will be collapsed and effectively
hidden from the user
-->
<summary style='text-decoration: underline'>Click here for alternative installation options</summary>
If there is a bugfix or feature that is not yet on CRAN, you can install it via
the {drat} package:


You can install {epidict} from the R4EPI repository:

```{r eval = FALSE}
# install.packages("drat")
drat::addRepo("R4EPI")
install.packages("epidict")
```

You can also install the in-development version from GitHub using the {remotes}
package (but there's no guarantee that it will be stable):

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("R4EPI/epidict") 
```

</details>


## Accessing dictionaries

There are four MSF outbreak dictionaries available in {epidict} based on DHIS2
exports:

 - Cholera/Acute watery diarrhea ("cholera")
 - Meningitis
 - Measles/Rubella ("measles")
 - Acute Jaundice Syndrome (often suspected to be Hepatitis E) ("ajs")

> You can read more about the outbreak dictionaries at <https://r4epis.netlify.com/outbreaks>

The dictionary can be obtained via the `msf_dict()` function, which specifies a
dictionary that describes recorded variables (`data_element_shortname`) in rows
and their possible options (if categorical):

```{r outbreak}
library("epidict")
msf_dict("Measles")
msf_dict("AJS")
msf_dict("Cholera")
msf_dict("Meningitis")
```

In addition, there are three MSF survey dictionaries available:

 - Retrospective mortality and access to care ("mortality")
 - Malnutrition ("nutrition") 
 - Vaccination Coverage ("vaccination")

> You can read more about the survey dictionaries at <https://r4epis.netlify.com/surveys>

These are accessible via `msf_dict_survey()` where the variables are in 
`name`.

```{r survey}
msf_dict_survey("Mortality")
# msf_dict_survey("Nutrition")
msf_dict_survey("Vaccination")
```

## Generating data

The {epidict} package has a function for generating data that's called
`gen_data()`, which takes three arguments: The dictionary, which column
describes the variable names, and how many rows are needed in the output.

```{r gendata}
gen_data("Measles", varnames = "data_element_shortname", numcases = 100, org = "MSF")
gen_data("Vaccination", varnames = "name", numcases = 100, org = "MSF")
```

## Cleaning data with the dictionaries

You can use the dictionaries to clean the data via the [{matchmaker}](https://www.repidemicsconsortium.org/matchmaker) package:

```{r lookup, message = FALSE}
library("matchmaker")
library("dplyr")

dat <- gen_data(dictionary = "Cholera", 
  varnames = "data_element_shortname",
  numcases = 20,
  org = "MSF"
)
print(dat)

# We want the expanded dictionary, so we will select `compact = FALSE`
dict <- msf_dict(disease = "Cholera", 
  long    = TRUE,
  compact = FALSE,
  tibble  = TRUE
)
print(dict)

# Now we can use matchmaker to filter the data
dat_clean <- matchmaker::match_df(dat, dict, 
  from  = "option_code",
  to    = "option_name",
  by    = "data_element_shortname",
  order = "option_order_in_set"
)
print(dat_clean)
```

